Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination

### 2020-09-10 AAMAS2021/minimax.tex
Table 2 and 3

\sisetup{round-mode=places, round-precision=2, table-figures-integer=1, table-figures-decimal=2}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 9.05 & 0.51 & 7.38 & 0.65 & 6.08 & 0.76\\
			40 & 7.3 & 0.62 & 4.21 & 1.18 & 2.77 & 1.27\\
			60 & 6.01 & 0.81 & 1.56 &0.98 & 1.23 & 1.22\\
			80 & 4.72 & 1.07 & 0.2 & 0.33 & 0.55 & 0.71\\
			100 & 3.0 & 0.97 & 0.0 &  0.0 & 0.2 & 0.28\\
			120 & 1.31 & 1.15 & 0.0 & 0.0 & 0.1 & 0.21\\
			140 & 0.44 & 0.85 & 0.0 & 0.0 & 0.1 & 0.21\\
			150 & 0.21 & 0.58 & 0.0 & 0.0 & 0.1 & 0.21\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Minimax regret in problems of size $(5, 10)$ after $k$ questions over $25$ runs.}
	\label{fig:55}
\end{table}

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd} & {sd} & {L.\ pes.} & {sd} \\
			\midrule
			0 & 20.0 & 0 & 20.0 & 0 \\
			20 & 19.985 & 0.042 & 18.770 & 0.111 \\
			40 & 19.903 & 0.080 & 17.659 & 0.290 \\
			60 & 19.764 & 0.159 & 16.951 & 0.541 \\
			80 & 19.403 & 0.221 & 15.736 & 0.367 \\
			100 & 18.947 & 0.383 & 14.621 & 0.703 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Regret in problems of size $(10, 20)$ after $k$ questions.}
	\label{fig:1020}
\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 & 5.02 & 0.82 & & \\
			50 & 6.47 & 1.14 & & \\
			100 & 9.4 & 1.58 & & \\
			150 &  & & & \\
			100 &  & & & \\
			125 &  & & & \\
			150 &  & & 12.31 & 0.96 \\
			200 &  & & 16.12 & 1.06 \\
			250 &  & & 20.0 & 0.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the committee.}
	\label{fig:p}
\end{table}

>>>>

\sisetup{round-mode=places, round-precision=2, table-figures-integer=1, table-figures-decimal=2}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 9.05 & 0.51 & 7.38 & 0.65 & 6.08 & 0.76\\
			40 & 7.3 & 0.62 & 4.21 & 1.18 & 2.77 & 1.27\\
			60 & 6.01 & 0.81 & 1.56 &0.98 & 1.23 & 1.22\\
			80 & 4.72 & 1.07 & 0.2 & 0.33 & 0.55 & 0.71\\
			100 & 3.0 & 0.97 & 0.0 &  0.0 & 0.2 & 0.28\\
			120 & 1.31 & 1.15 & 0.0 & 0.0 & 0.1 & 0.21\\
			140 & 0.44 & 0.85 & 0.0 & 0.0 & 0.1 & 0.21\\
			150 & 0.21 & 0.58 & 0.0 & 0.0 & 0.1 & 0.21\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average minimax regret in problems of size $(5, 10)$ after $k$ questions over $25$ runs.}
	\label{fig:55}
\end{table}

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd} & {sd} & {L.\ pes.} & {sd??} \\
			\midrule
			0 & 20.0 & 0.0 & 20.0 & 0.0 \\
			50 & 19.81 & 0.12 & 17.19 & 1.2 \\
			100 & 19.22 & 0.25 & 14.72 & 2.4 \\
			150 & 18.18 & 0.54 & 12.52 & 3.89 \\
			200 & 17.05  & 0.29 & 10.57 & 5.14 \\
			250 & 15.95 & 0.26 & 9.28 & 6.17 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $k$ questions over $5$ runs.}
	\label{fig:1020}
\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 & 5.02 & 0.82 & 3.21 & 1.6 \\
			25 & 5.83 & 1.25 & 6.79 & 1.2 \\
			50 & 6.47 & 1.14 & 5.2 & 1.58 \\
			100 & 9.4 & 1.58 & 8.66 & 0.51 \\
			150 & 11.89 & 1.1 & 12.31 & 0.96 \\
			200 & 15.64  & 0.52 & 16.12 & 1.06 \\
			250 & 20.0 & 0.0 & 20.0 & 0.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the committee.}
	\label{fig:p}
\end{table}
